---
title: "EX4-SNA"
author: "Motahhreh Nadimi"
date: "21/04/2020"
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: united
    highlight: tango    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




## Exercise 1
** Built an arbitrary two-mode network and retrieve the associated one-mode networks, What do the diagonal and off-diagonal entries mean?**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
library(igraph)
library(statnet)
set.seed(123)
n1 <- 6
n2 <- 5
n <- n1 + n2
# define the probability of connection among nodes of different sets
p <- .5
# generate random bipartite graph.
g <- sample_bipartite(n1, n2, type="Gnp", p = p, directed=FALSE)
g
# check the type attribute:
V(g)$type
AM <- get.incidence(g)
colnames(AM) <- c("M1","M2","M3","M4","M5")
row.names(AM) <- c("F1","F2","F3","F4","F5","F6")
b <- graph.incidence(AM)
AM
# define color and shape mappings.
col <- c("blue", "yellow")
shape <- c("circle", "square")

plot(b,
     vertex.color = col[as.numeric(V(b)$type)+1],
     vertex.shape = shape[as.numeric(V(b)$type)+1],layout=layout.bipartite,
     vertex.size=20)
  is_bipartite(g)
#alternative plotting , I just remove layout
plot(b,
  vertex.color = col[as.numeric(V(b)$type)+1],
  vertex.shape = shape[as.numeric(V(b)$type)+1],
  vertex.size=20)
is_bipartite(g)
 
```




**we project two mode graph to one mode graph**
```{r echo=TRUE,  message=FALSE, warning=FALSE}

g.pr <- bipartite.projection(b)

g.pr
g.side1 <-g.pr$proj1
g.side2 <- g.pr$proj2

get.adjacency(g.side1,sparse=FALSE,attr="weight")
get.adjacency(g.side2,sparse=FALSE,attr="weight")

#we plot each of the one mode network:
shapes <- c("circle","square")
colors <- c("blue","red")
op <- par(mfrow=c(1,2))
plot(g.side1,vertex.color="blue",
     vertex.shape="circle",main="side1",
     edge.width=E(g.side1)$weight*2,
     vertex.size=15,vertex.label.degree=-pi/2,
     vertex.label.dist=1.2,vertex.label.cex=1)
plot(g.side2,vertex.color="red",
     vertex.shape="square",main="side2",
     edge.width=E(g.side1)$weight*2,
     vertex.size=15,vertex.label.degree=-pi/2,
     vertex.label.dist=1.2,vertex.label.cex=1)
```

**What do the diagonal and off-diagonal entries mean?
The adjacency matrix of each one-mode projection
males are undirectly connected through thier shared friend.
M1 and M4 are indirectly connected through thier 2 common female friend
but M1 and M2 are indirectly connected via one female friend.**





## Exercise 2

**Use the Davis data (Davis.txt file from the first R Lab) and transform it in a hypergraph of an object of class network.**



**A hypergraph is just a graph G=(V,E) where V is the set of vertices (nodes)
and E is a subset of the powerset of V. It is a data structure.
So a common graph is just a hypergraph with rank 2. (i.e each set in E contains exactly two vertices). 
A directed hypergraph uses pairs (X,Y) as the edges where X and Y are sets.**
```{r echo=TRUE,  message=FALSE, warning=FALSE}

h1<-read.table("/home/elham/Desktop/rrrrrrrrrrrrrrrrr/SNA/R LAB March 30th-20200417/Davis.txt",header = T, row.names = 1)
h1
class(h1)
row.names(h1)
colnames(h1)
f <- network(h1, matrix = "incidence", hyper = TRUE, directed = FALSE, loops = TRUE, multiple = TRUE)
f[,]
#as.matrix(network(t(h1)),matrix.type = "incidence")
g <- igraph::graph_from_incidence_matrix(h1)
col <- c("blue", "yellow")
shape <- c("circle", "square")

plot(g,
     vertex.color = col[as.numeric(V(g)$type)+1],
     vertex.shape = shape[as.numeric(V(g)$type)+1],
     vertex.size=20)
is_bipartite(g)
#plot(g)
```




## Exercise 3
**By considering the data("faux.magnolia.high") in statnet 
and using the manipulation functions in the networkScript.R:**

**a. count how many isolates there are**

**b. add all possible edges among nodes with Race="Black" and plot the resulting network**

**c. delete all nodes with Race="natAm" and plot the resulting network**

**d. delete all neighborhood edges of the most connected node**

**e. creat  te the subgraphs of Females and Males**

```{r echo=TRUE,  message=FALSE, warning=FALSE}
data(faux.magnolia.high)
v<- faux.magnolia.high
v
class(v)

#summary(faux.magnolia.high)

#get.node.attr(faux.magnolia.high,'Race')

par(mar=c(0,0,0,0))
gplot(faux.magnolia.high,gmode="graph",vertex.cex=0.6,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="grey80",edge.lwd=0.02,
      thresh=0.01,jitter=TRUE, usecurve=TRUE)
```


**a. count how many isolates there are:from this output, we can see the # of isolated out is 524**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
table(component.dist(v)$csize)

```


**extra work.we can plot data regarding attribute RACE**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
plot(v, displayisolates = FALSE, vertex.col = "Race", vertex.cex = 0.7)

```






**b. add all possible edges among nodes with Race="Black" and plot the resulting networksummary(faux.magnolia.high)**
```{r echo=TRUE,  message=FALSE, warning=FALSE}

summary(v ~ edges) # Look at the $g(y)$ statistic for this model
list.vertex.attributes(v) # List all vertex attributes
gr <- v %v% "Race"
table(gr)

l <- get.inducedSubgraph(v,
                           which(v %v% "Race" == "Black"))
l
gplot(l,gmode="graph",vertex.cex=0.6,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="blue",edge.lwd=0.02,
      thresh=0.01,jitter=TRUE, usecurve=TRUE)

```



**c. delete all nodes with Race="natAm" and plot the resulting networkdelete.vertices() modifies the network in place!**


```{r echo=TRUE,  message=FALSE, warning=FALSE}
list.vertex.attributes(v)

del <- v %v% "Race"
n2 <- v %s% which(del== "NatAm")
n2
as.sociomatrix(n2)
gplot(n2,displaylabels=TRUE)
#now we should delete n2
delete.vertices(v, vid = which(v %v% "Race"=="NatAm"))
gr <- v %v% "Race"
table(gr)
```

**delete all neighborhood edges of the most connected node**

```{r echo=TRUE,  message=FALSE, warning=FALSE}

fmh <- faux.magnolia.high
fmh
degreedist(faux.magnolia.high)

Degree <- degree(fmh)     #Computing the  of each node
table(Degree)
#Degree
which(Degree == 16)

#or 
fmh.degreedist <- table(degree(fmh))
fmh.degreedist
#765
#991
fmh2 = delete.edges (fmh, get.edgeIDs(fmh,756, neighborhood = "in"))
fmh2
fmh3 = delete.edges (fmh2, get.edgeIDs(fmh2,991, neighborhood = "in"))
fmh3
```

**create the subgraphs of Females and Males**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
fmh <- faux.magnolia.high
fmh

#compare degree distributions by sex:
summary(fmh ~ degree(0:8, "Sex"))
list.vertex.attributes(fmh)
#t <- fmh %v% "Sex"
#Subgraoh of female
n1F <- get.inducedSubgraph(fmh, which(fmh %v% "Sex" == "M" ))
n1F
#subgraph of male.
n2F <- get.inducedSubgraph(fmh, which(fmh %v% "Sex" == "F" ))
n2F
```


```{r echo=TRUE,  message=FALSE, warning=FALSE}
```
**THANK YOU**

```{r echo=TRUE,  message=FALSE, warning=FALSE}
```


```{r echo=TRUE,  message=FALSE, warning=FALSE}
```

