---
title: "EX3-SNA"
author: "Motahhreh Nadimi"
date: "4/3/2020"
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: united
    highlight: tango    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




## Exercise 1.1
**Star Network**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
library(statnet)
g <- network.initialize(15) 
g
g[1,] <- 1 #Add an edge from 1 to ALL
par(mar=c(0,0,0,0))
gplot(g,gmode="graph",vertex.cex=1,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="grey80",edge.lwd=0.02,
       thresh=0.01,jitter=TRUE, usecurve=FALSE)
```




**Complete Network**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
g <- network.initialize(10) #Create an empty graph
g[,] <- 1 
par(mar=c(0,0,0,0))
gplot(g,gmode="graph",vertex.cex=1,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="grey80",edge.lwd=0.02,
       thresh=0.01,jitter=TRUE, usecurve=FALSE)
```

**Circle Network**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
n<-50  #fill the N , N is number of nodes 
g <- network.initialize(n) #Create an empty graph
g
mat<-as.sociomatrix(g)
#mat
mat[row(mat) == col(mat)-1] <-mat[n,1] <- 1 # change entries 
#mat
g[,]<-mat # using replacement operators
#summary(g)
#g[1,2] <- g[2,3] <- g[3,4] <- g[4,5] <-g[5,1] <- 1 
par(mar=c(0,0,0,0))
gplot(g,gmode="graph",vertex.cex=0.6,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="grey80",edge.lwd=0.02,
      thresh=0.01,jitter=TRUE, usecurve=FALSE,mode='circle')
```




**Line network**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
n<-30  #fill the N , N is number of nodes 
g <- network.initialize(n) #Create an empty graph
g
mat<-as.sociomatrix(g)
#mat
mat[row(mat) == col(mat)-1] <- 1 # change entries 
#mat
g[,]<-mat # using replacement operators
#summary(g)
#g[1,2] <- g[2,3] <- g[3,4] <- g[4,5] <-g[5,1] <- 1 
par(mar=c(0,0,0,0))
gplot(g,gmode="graph",vertex.cex=1,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="grey80",edge.lwd=0.02,
       thresh=0.01,jitter=TRUE, usecurve=FALSE,mode='kamadakawai')
```






## Exercise 1.2

**a) write a R function for each type of graph allowing the user 
to generate graphs with an arbitrary number of nodes.
b) Running the above R functions to show the adjacency matrix of 
each type of graph having not less than 100 nodes.
NOTE: Graphs must be stored as R objects of class “network”**

**Complete Graph** 
```{r echo=TRUE,  message=FALSE, warning=FALSE}
n<- 100 # n is # of nodes
randomG <- rgraph(n, m=1, tprob=1, mode="digraph") # Create a random graph with n=7 nodes and tie prob = 0.5
generate <- function(randomG) {
  output <-as.network(randomG)
  add.edges(output,row(randomG)[randomG>0],col(randomG)[randomG>0])
  par(mar=c(0,0,0,0))
  gplot(output,gmode="graph",vertex.cex=1,
        vertex.col=rgb(0,0,139,alpha=80,
                       maxColorValue=255),
        edge.col="grey80",edge.lwd=0.02,
         thresh=0.01,jitter=TRUE, usecurve=FALSE,mode = 'circle')
  return(output)
}
generate(randomG)
d<-as.sociomatrix(randomG) #showing the adjecncy matrix 
d[1:10,1:10]
output <-as.network(randomG)
```






**star graph**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
n<-300 # fill the n
randomG <- rgraph(n, m=1, tprob=0, mode="graph") # Create a random graph with n=7 nodes and tie prob = 0.5
randomG[,1] <-randomG[1,] <- 1
generate <- function(randomG) {
  output <-as.network(randomG)
  add.edges(output,row(randomG)[randomG>0],col(randomG)[randomG>0])
  par(mar=c(0,0,0,0))
  gplot(output,gmode="graph",vertex.cex=1,
        vertex.col=rgb(0,0,139,alpha=80,
                       maxColorValue=255),
        edge.col="grey80",edge.lwd=0.02,
         thresh=0.01,jitter=TRUE, usecurve=FALSE)
  return(output)
}
generate(randomG)
d<-as.sociomatrix(randomG) #showing the adjecncy matrix 
d[1:10,1:10]
```






**Circle graph or ring graph**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
n<- 100
m <- rgraph(n, m=1, tprob=0, mode="graph")
m[row(m) == col(m)-1] <-m[n,1] <- 1 # change entries 
m[1:5,1:5]
generate <- function(m) {
  output <-as.network(m)
  add.edges(output,row(m)[m>0],col(m)[m>0])
  par(mar=c(0,0,0,0))
  gplot(output,gmode="graph",vertex.cex=0.6,
        vertex.col=rgb(0,0,139,alpha=80,
                       maxColorValue=255),
        edge.col="grey80",edge.lwd=0.02,
         thresh=0.01,jitter=TRUE, usecurve=FALSE, mode = 'circle')
  return(output)
}
generate(m)
d<-as.sociomatrix(randomG) #showing the adjecncy matrix 
d[1:10,1:10]
```






**line graph**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
#.................................................
n<- 100
m <- rgraph(n, m=1, tprob=0, mode="graph")
m[row(m) == col(m)-1] <- 1 # change entries 
m[1:5,1:5]

generate <- function(m) {
  output <-as.network(m)
  add.edges(output,row(m)[m>0],col(m)[m>0])
  gplot(output,gmode="graph",vertex.cex=1,
        vertex.col=rgb(0,0,139,alpha=80,
                       maxColorValue=255),
        edge.col="grey80",edge.lwd=0.02,
       thresh=0.01,jitter=TRUE, usecurve=FALSE,mode='kamadakawai')
  return(output)
}
generate(m)
d<-as.sociomatrix(randomG) #showing the adjecncy matrix 
d[1:10,1:10]
```





## Exercise 2.1




**Generate a directed cyclic circle graph of the same size of
the circle graph created in exercise 1.
(again this should be stored in an object of network class)**




**try with 10 nodes**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
n<-10
m <- rgraph(n, m=1, tprob=0, mode="digraph")
m[1:5,1:5]
m[row(m) == col(m)-1] <-m[n,1] <- 1 # change entries 
m[5,2]<-m[2,4]<-m[4,5] <- 1 # change entries 
m[9,4]<-m[4,7]<-m[7,9] <- 1 # change entries 

m
g <- network(m, directed=TRUE,loops=TRUE,matrix.type="adjacency")
summary(g)
gplot(g,gmode="digraph",vertex.cex=1,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="grey80",edge.lwd=0.02,
     thresh=0.01,jitter=TRUE, usecurve=FALSE,mode='circle')
```





**code with 100 nodes**
```{r echo=TRUE,  message=FALSE, warning=FALSE}
n<-100
m <- rgraph(n, m=1, tprob=0, mode="digraph")
m[row(m) == col(m)-1] <-m[n,1] <- 1 # change entries 
m[99,2]<-m[2,50]<-m[50,99] <- 1 # change entries 
m[9,24]<-m[24,79]<-m[79,9] <- 1 # change entries 
g <- network(m, directed=TRUE,loops=TRUE,matrix.type="adjacency")
#summary(g)

par(mar=c(0,0,0,0))

gplot(g,gmode="digraph",vertex.cex=0.5,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="grey80",edge.lwd=0.02,
       thresh=0.01,jitter=TRUE, usecurve=FALSE,mode='circle')
```





## Exercise 3.1

**Running the following lines setting  num_nodes not less than 100
my_adjacency <- matrix(round(runif(num_nodes*num_nodes)), nrow = num_nodes, ncol = num_nodes)
edge_weights <- round(runif(num_edges, min = 1, max = 5))

a) Create an undirected graph as an object of class network having 
the edge_weights as edge attributes.

b) By using only the functions reported in the Basic summaries and
elementary operations section of the R script of the 30th March R lab 
(approx. from line 72 of the R script) computing the network density

c) What is the value of the network density if we consider the edge weights?**

```{r echo=TRUE,  message=FALSE, warning=FALSE}

my_adjacency <- matrix(round(runif(100*100)), nrow = 100, ncol = 100)
#g<-network.initialize(100) #Initialize the network
#g[,]<-my_adjacency # using  replacement operators (not a good solution)
g<-network(my_adjacency,matrix.type="adjacency")
g[1:5,1:5]

par(mar=c(0,0,0,0))
gplot(g,gmode="graph",vertex.cex=0.6,
      vertex.col=rgb(0,0,139,alpha=80,
                     maxColorValue=255),
      edge.col="grey80",edge.lwd=0.02,
    thresh=0.01,jitter=TRUE, usecurve=TRUE,mode='circle')
#edge_weights <- round(runif(num, min = 1, max = 5))
list.edge.attributes(g)
num<-network.edgecount(g, na.omit = TRUE)
num
#Assign some attributes
# In statnet, the actual values of
#the valued ties are stored in an edge attribute
set.edge.attribute(g,"rndval",
                   runif(num, min = 1, max = 5))
#summary(g %e% "rndval")
f<-as.sociomatrix(g)
f[1:10,1:10]
list.edge.attributes(g)
c<-round(get.edge.attribute(g, "rndval"))
c[1:10]
network.dyadcount(g) # How many dyads in nrelations?
num # number of edge
density<- 4996/(100*99)
density
#or
gden(g,ignore.eval=TRUE)

```



**The function edge_density of irgraph does not consider weights.
If you call it on a weighted graph, it treats the graph as
unweighted and returns the density:$nb_edges / V*(V-1) for$
directed graphs, and $nb_edges / V*(V-1) / 2 for$ undirected grapsh**


```{r echo=TRUE,  message=FALSE, warning=FALSE}
```

**Thank You**

```{r echo=TRUE,  message=FALSE, warning=FALSE}
```


```{r echo=TRUE,  message=FALSE, warning=FALSE}
```


```{r echo=TRUE,  message=FALSE, warning=FALSE}
```


```{r echo=TRUE,  message=FALSE, warning=FALSE}
```


```{r echo=TRUE,  message=FALSE, warning=FALSE}
```

